Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-26 ConferencePaper/DraftEdwardsWoods.Rnw
Pulled almost all figures and tables out so it would compile.  Working on all the fixes.

\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
<<echo=false,fig=TRUE>>=
library(ggplot2)
#qplot(KWH, data = RECS, xlim=c(0,30000),facets =EthRace~KOWNRENT, geom = "density" )
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Annual kWh by Income}
\label{fig:kWhbyIncome}
<<echo=false,fig=TRUE>>=
library(ggplot2)
#qplot(Income,KWH, data = RECS, xlim=c(0,30000),facets =EthRace~KOWNRENT )+geom_boxplot()
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
<<echo=false,fig=TRUE>>=
#qplot(NHSLDMEM,data=RECS,facets =~EthRace, geom = "density",title="Household Size by Race and Ethnicity")+xlab("Household Size")
@
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
<<echo=false,fig=TRUE>>=
#qplot(YEARMADE,data=RECS,facets =KOWNRENT~EthRace, geom = "density",)
@
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
<<echo=false,fig=TRUE>>=
#boxplot(TEMPHOME~EthRace, notch=TRUE,data=RECS)
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Daytime Temp When Away and Race/Ethnicity (Winter)}
\label{fig:DayAwayRace}
#boxplot(TEMPGONE~EthRace, notch=TRUE,data=RECS)
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Nightime Temp and Race/Ethnicity (Winter)}
\label{fig:NightRace}
<<echo=false,fig=TRUE>>=
#boxplot(TEMPNITE~EthRace, notch=TRUE,data=RECS)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Daytime Temp Home by Race/Ethnicity (Summer)}
\label{fig:HomeRaceS}
<<echo=false,fig=TRUE>>=
#boxplot(TEMPHOMEAC~EthRace, notch=TRUE,data=RECS)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Day Temp Away by Race/Ethnicity (Summer)}
\label{fig:AwayRaceS}
<<echo=false,fig=TRUE>>=
#boxplot(TEMPGONEAC~EthRace, notch=TRUE,data=RECS)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Nightime Temp and Race/Ethnicity (Summer)}
\label{fig:NightRaceS}
<<echo=false,fig=TRUE>>=
#boxplot(TEMPNITEAC~EthRace, notch=TRUE,data=RECS)
@
\end{center}
\end{figure}

@@

%Fix the Latex part of this.
% Since all the parameters are statistically significant it is easier to show the effects of our measure of housing market discrimination on the probability of each structure and tenure choice for the race and ethnicity combinations.  The HUD reports run from \Sexp{min(HUDCut[3])} complaints per 100,000 to \Sexp{max(HUDCut[3])} complaints per 100,000.  Figure \ref{fig:HUDOnChoice} shows the reaction to HUD complaints over the 1 to 21 complaint range.

\begin{figure}
\begin{center}\label{fig:HUDOnChoice}

<<echo=false,fig=TRUE>>=
# Need to figure this figure out.  It may be very complex

@
\end{center}
\end{figure}

@@

\appendix
\section{Orthodox Results}\label{OrthResults}

>>>>

% \begin{figure}
% \begin{center}
% \caption{Annual kWh by Rent/Own and Race}
% \label{fig:kWhbyOwnRace}
% <<echo=false,fig=TRUE>>=
% library(ggplot2)
% #qplot(KWH, data = RECS, xlim=c(0,30000),facets =EthRace~KOWNRENT, geom = "density" )
% @
% \end{center}
% \end{figure}

% \begin{figure}
% \begin{center}
% \caption{Annual kWh by Income}
% \label{fig:kWhbyIncome}
% <<echo=false,fig=TRUE>>=
% library(ggplot2)
% #qplot(Income,KWH, data = RECS, xlim=c(0,30000),facets =EthRace~KOWNRENT )+geom_boxplot()
% @
% \end{center}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<echo=false,fig=TRUE>>=
% #qplot(NHSLDMEM,data=RECS,facets =~EthRace, geom = "density",title="Household Size by Race and Ethnicity")+xlab("Household Size")
% @
% \end{center}
% \end{figure}

@@

% \begin{figure}
% \begin{center}
% \caption{Age of Structure by Rent/Own and Race/Ethnicity}
% \label{fig:AgebyOwnRace}
% <<echo=false,fig=TRUE>>=
% #qplot(YEARMADE,data=RECS,facets =KOWNRENT~EthRace, geom = "density",)
% @
% \end{center}
% \end{figure}

@@

% \begin{figure}
% \begin{center}
% \caption{Daytime Temp and Race/Ethnicity (Winter)}
% \label{fig:TempHomeRace}
% <<echo=false,fig=TRUE>>=
% #boxplot(TEMPHOME~EthRace, notch=TRUE,data=RECS)
% @
% \end{center}
% \end{figure}

% \begin{figure}
% \begin{center}
% \caption{Daytime Temp When Away and Race/Ethnicity (Winter)}
% \label{fig:DayAwayRace}
% #boxplot(TEMPGONE~EthRace, notch=TRUE,data=RECS)
% @
% \end{center}
% \end{figure}
% 
% 
% \begin{figure}
% \begin{center}
% \caption{Nightime Temp and Race/Ethnicity (Winter)}
% \label{fig:NightRace}
% <<echo=false,fig=TRUE>>=
% #boxplot(TEMPNITE~EthRace, notch=TRUE,data=RECS)
% 
% @
% \end{center}
% \end{figure}

% \begin{figure}
% \begin{center}
% \caption{Daytime Temp Home by Race/Ethnicity (Summer)}
% \label{fig:HomeRaceS}
% <<echo=false,fig=TRUE>>=
% #boxplot(TEMPHOMEAC~EthRace, notch=TRUE,data=RECS)
% 
% @
% \end{center}
% \end{figure}
% 
% 
% \begin{figure}
% \begin{center}
% \caption{Day Temp Away by Race/Ethnicity (Summer)}
% \label{fig:AwayRaceS}
% <<echo=false,fig=TRUE>>=
% #boxplot(TEMPGONEAC~EthRace, notch=TRUE,data=RECS)
% 
% @
% \end{center}
% \end{figure}
% 
% 
% \begin{figure}
% \begin{center}
% \caption{Nightime Temp and Race/Ethnicity (Summer)}
% \label{fig:NightRaceS}
% <<echo=false,fig=TRUE>>=
% #boxplot(TEMPNITEAC~EthRace, notch=TRUE,data=RECS)
% @
% \end{center}
% \end{figure}

@@

%Fix the Latex part of this.
Since all the parameters are statistically significant it is easier to show the effects of our measure of housing market discrimination on the probability of each structure and tenure choice for the race and ethnicity combinations.  The HUD reports run from \Sexpr{min(HUDCut[3])} complaints per 100,000 to \Sexpr{max(HUDCut[3])} complaints per 100,000.  Figure 
% \ref{fig:HUDOnChoice} 
shows the reaction to HUD complaints over the 1 to 21 complaint range.

% 
% \begin{figure}
% \begin{center}\label{fig:HUDOnChoice}
% 
% <<echo=false,fig=TRUE>>=
% # Need to figure this figure out.  It may be very complex
% 
% @
% \end{center}
% \end{figure}

@@

% \appendix
\section{Orthodox Results}\label{OrthResults}
